%-------------------------
% Resume in Latex
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Pedro Roa Cuevas} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:proacuevas@gmail.com}{\underline{proacuevas@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/pedroroac/}{\underline{linkedin.com/in/pedroroac}} $|$
    \href{https://github.com/Pedroroac}{\underline{github.com/pedroroac}}
\end{center}

%
%-----------Profile-----------
% \section{Profile}
\small DevOps Engineer with 5+ years of experience optimizing cloud environments, automating infrastructure, 
and enhancing system reliability. Expertise in Kubernetes, CI/CD pipelines, and cost optimization, with 
a proven track record of driving efficiency and reducing operational overhead.

%
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0.10in, label={}]
    \small{\item{
     \textbf{Cloud \& Infrastructure}{: Kubernetes, Istio/Service Mesh, Google Cloud, Azure, Terraform, Ansible} \\
     \textbf{CI/CD \& Automation}{: Git, ArgoCD, GitHub Actions, GitLab CI/CD, Bitbucket Pipelines, Helm, Kustomize} \\
     \textbf{Monitoring \& Security}{: Datadog, Hashicorp Vault, SonarQube, Snyk, Gatekeeper, Cybersecurity,
     Incident Response} \\
     \textbf{Development \& Scripting}{: Bash, Python}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Work Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Senior DevOps Engineer}{Jan 2025 -- Present}
      {OMERS}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Supported a GitHub repository migration by transitioning CI/CD pipelines to GitHub Actions, integrating automated code scanning for security and compliance, and enhancing development tooling to improve workflow efficiency and reliability.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
  %  \resumeSubSubheading
  %   {DevOps Engineer}{Jan 2023 -- Jan 2025}
  %   \resumeItemListStart
  %      \resumeItem{Apache Beam}
  %        {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
  %   \resumeItemListEnd
%-------------------------------------------
    \resumeSubheading
      {DevOps Engineer}{Jan 2023 -- Jan 2025}
      {OMERS}{Toronto, ON}
      \resumeItemListStart
        \resumeItem{Optimized Kubernetes upgrade process, achieving a 50\% reduction in upgrade times, enhancing overall system reliability and deployment speed.}
        \resumeItem{Fully automated the Kubernetes upgrade process using rollout sequences, upgrade channels, and cloud-based monitoring functions, leading to more consistent and reliable deployments.}
        % \resumeItem{Deployed comprehensive backup solution for Google Kubernetes Engine (GKE), ensuring high availability and data integrity.}
        \resumeItem{Scaled Kubernetes cluster capacity to meet growing application demands, significantly improving system performance and resource utilization.}
        \resumeItem{Achieved up to 50\% compute cost savings through the implementation of Cast AI, optimizing resource allocation and reducing operational expenses.}
        \resumeItem{Designed and provisioned production-ready Kubernetes clusters, ensuring high availability and optimal performance for mission-critical applications.}
        \resumeItem{Improved infrastructure security by automating vulnerability scans and redesigning traffic ingress into the Kubernetes cluster, leading to a stronger, more resilient system.}
        \resumeItem{Automated the certificate renewal process with CertManager, ensuring continuous security without manual intervention.}
        \resumeItem{Migrated the in-cluster Istio service mesh to a cloud-managed solution, enabling automated upgrades and reducing maintenance overhead.}
        % \resumeItem{Streamlined the deployment of observability agents on cloud VMs using Ansible.}
    \resumeItemListEnd

    \resumeSubheading
      {DevOps Engineer}{Jun 2022 -- Dec 2022}
      {Xhinola}{Remote}
      \resumeItemListStart
        \resumeItem{Led the migration of a payments application from Digital Ocean to Google Cloud, including containerizing the frontend, backend, and admin portal in Kubernetes.}
        \resumeItem{Strengthened cloud security by resolving critical vulnerabilities and implementing best practices.}
        \resumeItem{Integrated data analytics and visualization services into the infrastructure for better monitoring.}
      \resumeItemListEnd
    
      \resumeSubheading
      {Network Operations Center Analyst}{Mar 2020 -- Dec 2021}
      {Kaleyra}{Remote}
      \resumeItemListStart
        \resumeItem{Provided technical support to customers, troubleshooting and resolving system issues across enterprise networks.}
        \resumeItem{Prioritize remediation of issues in a 24 x 7 environment with critical uptime requirements.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Postgraduate Certificate, Cybersecurity}{Ontario, CA}
      {Loyalist College School of Applied Sciences, Skills, and Technology}{2022 -- 2023}
    \resumeSubheading
      {Bachelor's Degree, Telematics Engineering}{Santo Domingo, DR}
      {Pontificia Universidad Católica Madre y Maestra (PUCMM)}{2016 -- 2019}
  \resumeSubHeadingListEnd

%-----------CERTIFICATIONS-----------
\section{Certifications}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{\href{https://www.credly.com/badges/20f3fe7f-c039-4334-9a88-639dea316962?source=linked_in_profile}{CKA: Certified Kubernetes Administrator}}}{2022 -- 2025}
      \resumeProjectHeading
          {\textbf{\href{https://www.credly.com/badges/93cb6253-339f-4468-b5e8-a77ede695361?source=linked_in_profile}{LFCS: Linux Foundation Certified Systems Administrator}}}{2021 -- 2024}
    \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}